\documentclass[letterpaper]{article}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[some]{background}
\usepackage{lipsum}

\definecolor{titlepagecolor}{cmyk}{1,.60,0,.40}
\definecolor{titlepagecolor2}{rgb}{19, 62, 135}

\DeclareFixedFont{\bigsf}{T1}{phv}{b}{n}{1.5cm}

\backgroundsetup{scale=1,angle=0,opacity=1,contents={\begin{tikzpicture}[remember picture,overlay]
 \path [fill=titlepagecolor] (-0.5\paperwidth,5) rectangle (0.5\paperwidth,10);  
\end{tikzpicture}}
}
\makeatletter
\def\printauthor{%                  
    {\large \@author}}              
\makeatother
\author{%
    Gagik Gavalian \\
    Harut Avakian \\
    Patrick Achenbach \\
    Richard Tyson \\
    \textit{Jefferson Lab, Newport News, VA, USA }\vspace{40pt} \\
     Aleksandr Privalov \\
    \textit{NIIChaVo}
    }
\begin{document}
\begin{titlepage}
\BgThispage
\newgeometry{left=1cm,right=4cm}
\vspace*{4cm}
\noindent
\textcolor{white}{
%\bigsf
\huge 
\textsf{Integration of AI/ML in experimental data  lifecycle in CLAS12}}
\vspace*{2.5cm}\par
\noindent
\begin{minipage}{0.35\linewidth}
    \begin{flushright}
        \printauthor
    \end{flushright}
\end{minipage} \hspace{15pt}
%
\begin{minipage}{0.02\linewidth}
    \rule{1pt}{175pt}
\end{minipage} \hspace{-10pt}
%
\begin{minipage}{0.8\linewidth}
\vspace{5pt}
    \begin{abstract} 
 Artificial Intelligence and Machine Learning (AI/ML) algorithms have seen a variety of implemented 
    and proof-of-concept applications at the CEBAF Large Acceptance Spectrometer at 12 GeV (CLAS12) located 
    at the Continuous Electron Beam Accelerator Facility (CEBAF). Past applications have focused on data-taking, 
    reconstruction, simulation, and data analysis, whilst several other stages in the process chain will benefit 
    from the full application of AI/ML. This paper introduces a proposal to combine the existing 
    wealth of experience and applications at CLAS12 and implement novel AI/ML-based solutions where they are missing. 
    This implementation aims to improve the overall experimental life cycle, minimizing the time required to produce and 
    publish higher-quality data compared to existing paradigms. This will transform a human-driven nuclear 
    physics experiment into a fully AI/ML-assisted one
    \end{abstract}
\end{minipage}
\end{titlepage}
\restoregeometry

%\lipsum[1-2]



\input{introduction}

\input{dataacquisition}

\input{detectormonitoring}

\input{reconstruction}

\input{physicsanalysis}

\input{large_language_models}


\input{projects}
%\input{data_analysis_data}
%\input{results}

\input{summary}


\begin{thebibliography}{00}
\bibitem{AITracking}
P. Thomadakis, A. Angelopoulos, G. Gavalian, \emph{et. al.}, \emph{Comput. Phys. Commun.} \textbf{276} 108360 (2022).

\bibitem{AITracking2}
G. Gavalian, \emph{et. al.}, R. De Vita, V. Ziegler, \emph{ArXiv e-prints} arXiv:2202.06869 (2022).

\bibitem{AIDenoising}
P. Thomadakis, A. Angelopoulos, G. Gavalian, \emph{et. al.}, \emph{Comput. Phys. Commun.} \textbf{271} 108201 (2022).

\bibitem{FastSim}
D. Darulis, R. Tyson, \emph{et. al.}, \emph{ArXiv e-prints} arXiv:2207.11254 (2022).

\bibitem{InstaRec}
G. Gavalian, \emph{JINST} \textbf{19} C05050 (2024).

\bibitem{Hydra}
T. Jeske, \emph{et. al.}, \emph{EPJ Web of Conf.} \textbf{295} 02008 (2024).

\end{thebibliography}

\end{document}
